Numerous variables relating to 2016 election in 2021 US GSS

### 2022-03-18 outputs/paper/paper.Rmd
gg plot and added tax

reduced_data %>%
  ggplot(aes(x = gender, fill = gender)) +
  geom_bar() +
  scale_fill_brewer(palette = "Blues")

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  scale_fill_brewer(palette = "yellow")

@@

@@

In general, similar to the indicators above, Hillary Clinton supporters were moved by social equality such as 
"Assistance to the Poor", "nation welfare", "nation education" and "Assistance to the other countries". On the other hand, Donald Trump supporters were interested by more conservative ideas that US is spending too much on the sessions above.

>>>>

reduced_data %>%
  ggplot(aes(x = gender, fill = gender)) +
  geom_bar() +
  scale_fill_brewer(palette = "pink")

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  scale_fill_brewer(palette = "green")

@@

reduced_data$tax <- factor(reduced_data$tax, levels = c("Too low","About right","Too high"))
reduced_data %>%
  ggplot(aes(x = tax, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

@@

In general, similar to the indicators above, Hillary Clinton supporters were moved by improvement in social equality or welfare such as 
"Assistance to the Poor", "nation welfare", "nation education" and "Assistance to the other countries". On the other hand, Donald Trump supporters were interested by more conservative ideas that US is spending too much on the sessions above.
